\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-09-28 draft.tex
broad reorganization of sec:main

\bigskip
\subsection{The Renewal Decision}
\label{sec:break}

@@

Since I focus on symmetric equilibria, any increase in $\tau^a$ is accompanied by an equal increase in $\tau^{*a}$. Combining the impact of the home and foreign tariff when the two are constrained to be equal:
\begin{lemma}
	Holding lobbying effort constant, the probability the legislature breaks a trade agreement is weakly decreasing in $\bta$ (i.e. $\frac{\partial b(e,\bta)}{\partial  \tau^a} + \frac{\partial b(e,\bta)}{\partial  \tau^{*a}} \leq 0$).
	\label{res:bcomb}
\end{lemma}

\noindent The legislature's bias toward the import-competing industry overweights the negative impact of the home tariff on the break probability and ensures this result.

\subsubsection{Lobby}
\label{sec:lob_un}
The lobby chooses its level of effort as a function of $\bta$, given the implications of that choice on the legislature's probability of breaking the agreement. The lobby maximizes probability-weighted profits net of effort:
\[
  \max_{e} b(e,\bta) \left[\pi(\tau^n) - e_n \right] + [1 - b(e,\bta)] \pi(\tau^a) - e
\]
The first order condition shows that the lobby balances the cost of an extra dollar of expenditure with the higher profits from a trade war weighted by the increase in the probability of provoking the trade war:
\begin{equation}
	\frac{\partial b(e,\bta)}{\partial e} \left[ \pi(\tau^n) -e_n - \pi(\tau^a) \right] = 1 
	\label{eq:lobbyfoc}
\end{equation}
Assumption [old assumption3] and Result~\ref{res:bincC} ensure the second order condition. To guarantee an interior solution, we need
  \begin{equation}
	  \frac{\partial b(0,\bta)}{\partial e} \left[ \pi(\tau^n) -e_n- \pi(\tau^a) \right] > 1.
		\label{ine:lobint}	
  \end{equation}
If the executives were to set $\tau^a = \tau^n$, there would be no incentive for the lobby to make a positive contribution. There are some other cases in which it is in the executives' interest to set trade agreement tariffs so as to disengage the lobby. The following results only hold when the marginal impact of the first lobbying dollar on the break probability is sufficiently high to make engaging in the political process worthwhile for the lobby.

@@

\subsection{The Trade Agreement}
\label{sec:ta}
I represent the probability that the trade agreement will be broken as $B(\bta)=b(e(\bta),\bta)$ where $e(\bta)$ is the best response function implicit in Equation \ref{eq:lobbyfoc}, the lobby's first order condition.

@@

\noindent When the executives raise $\bta$ the legislature becomes less likely to abrogate the agreement, for three reasons. First, the legislature prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $B(\bta)$ indirectly (Result~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the legislature's preferred tariff further (Lemma~\ref{res:bcomb}). Thus, beyond promising a lower tariff from the trading partner, we can think of the trade agreement as a sort of political commitment device that can be used to reduce political pressure and therefore get the legislature to maintain a lower tariff than it otherwise would.

@@

>>>>

\vskip1in

@@

The lobby chooses its level of effort as a function of $\bta$, given the implications of that choice on the legislature's probability of breaking the agreement. The lobby maximizes probability-weighted profits net of effort:
\[
  \max_{e} b(e,\bta) \left[\pi(\tau^n) - e_n \right] + [1 - b(e,\bta)] \pi(\tau^a) - e
\]
The first order condition shows that the lobby balances the cost of an extra dollar of expenditure with the higher profits from a trade war weighted by the increase in the probability of provoking the trade war:
\begin{equation}
	\frac{\partial b(e,\bta)}{\partial e} \left[ \pi(\tau^n) -e_n - \pi(\tau^a) \right] = 1 
	\label{eq:lobbyfoc}
\end{equation}
Assumption [old assumption3] and Result~\ref{res:bincC} ensure the second order condition. To guarantee an interior solution, we need
  \begin{equation}
	  \frac{\partial b(0,\bta)}{\partial e} \left[ \pi(\tau^n) -e_n- \pi(\tau^a) \right] > 1.
		\label{ine:lobint}	
  \end{equation}
If the executives were to set $\tau^a = \tau^n$, there would be no incentive for the lobby to make a positive contribution. There are some other cases in which it is in the executives' interest to set trade agreement tariffs so as to disengage the lobby. The following results only hold when the marginal impact of the first lobbying dollar on the break probability is sufficiently high to make engaging in the political process worthwhile for the lobby.

@@

I represent the probability that the trade agreement will be broken as $B(\bta)=b(e(\bta),\bta)$ where $e(\bta)$ is the best response function implicit in Equation \ref{eq:lobbyfoc}, the lobby's first order condition.

@@

\noindent When the executives raise $\bta$ the legislature becomes less likely to abrogate the agreement, for three reasons. First, the legislature prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $B(\bta)$ indirectly (Result~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the legislature's preferred tariff further (Lemma~\ref{res:leg_a}). Thus, beyond promising a lower tariff from the trading partner, we can think of the trade agreement as a sort of political commitment device that can be used to reduce political pressure and therefore get the legislature to maintain a lower tariff than it otherwise would.

@@

\bigskip
\subsection{Foreign Trade Agreement Tariffs}
\label{sec:foreign}

\bigskip
\subsection{Home Trade Agreement Tariffs}
\label{sec:home}
